### 2018-02-12 Writing/Thesis/content/chapter-fundamentals.tex
even more writing

Suppose an aspiring gardener wants to learn how to distinguish between different species of iris plants, a genus of ornamental plants with colorful flowers. More specifically, the focus lies on the three species iris versicolor, virginica and setosa. In order to do so, the gardener has observed four different \textit{features}, namely the length and width of their petals and sepals, for a number of different individuals for which he knows the species, which is illustrated in Table \ref{tab:iris}. The goal of the gardener is then to learn how to distinguish the species based on these features, that is to derive a \textit{model} from the data that will predict which species (out of the considered three) an unknown iris plant is. The gardener decides to build a decision tree from the data with forks on the basis of feature values, so that they can determine the species of the plant without much calculation. They observe that all iris setosa plants from his sample have a petal width of $\leq 0.6 $ cm, and that of the plants with a petal width of $>0.6$ cm, most plants with a petal width $\leq 1.7$ cm are of the iris versicolor species. The remaining plants with a petal width of $>1.7$ cm are mostly iris virginica plants. While this model will not correctly predict the species of all iris plants, the gardener is settles with the approximation they have found.

@@

In formal terms, the gardener is searching for an unknown \textit{target function} $f:X \rightarrow Y$ from the input space $X$ to the output space $Y$ that represents an ideal way of identifying iris species \cite{abu2012learning}. $X$ denotes the possible inputs, in this case all combinations of the four features that have been defined, whereas $Y$ are the outputs, here the species of iris plant. The examples that the gardener recorded are samples $(x_1,y_1),(x_2,y_2),\dots,(x_n,y_n)$ from $f$ such that $f(x_i)=y_i$. Together, they form a data set $D$ which is one of all possible data sets $\mathbb{D}$ for the problem. They then choose a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees. The learning algorithm itself thus maps a data set to a hypothesis from the hypothesis space and can be defined as $A:\mathbb{D}\rightarrow H$.

%TODO include picture of the decision tree that is built & of the general ML-Model (from book)

@@

>>>>

Suppose an aspiring gardener wants to learn how to distinguish between different species of iris plants, a genus of ornamental plants with colorful flowers. More specifically, the focus lies on the three species iris versicolor, virginica and setosa. In order to do so, the gardener has observed four different \textit{features}, namely the length and width of their petals and sepals, for a number of different individuals for which he knows the species, which is illustrated in Table \ref{tab:iris}. The goal of the gardener is then to learn how to distinguish the species based on these features, that is to derive a \textit{model} from the data that will predict which species (out of the considered three) an unknown iris plant is. The gardener decides to build a decision tree from the data with forks on the basis of feature values, so that they can determine the species of the plant without much calculation. They observe that all iris setosa plants from his sample have a petal width of $\leq 0.6 $ cm, and that of the plants with a petal width of $>0.6$ cm, most plants with a petal width $\leq 1.7$ cm are of the iris versicolor species. The remaining plants with a petal width of $>1.7$ cm are mostly iris virginica plants. While this model (illustrated in Fig. \ref{fig:decision_tree}) will not correctly predict the species of all iris plants, the gardener is settles with the approximation they have found.

@@

%\tikzsetnextfilename{DecisionTree}
\begin{figure}
\includegraphics[width=\textwidth]{gfx/placeholder_decisionTree}
\caption{PLACEHOLDER: The decision tree constructed as a simple model in the gardening example to classify iris species}
\label{fig:decision_tree}
\end{figure}

In formal terms, the gardener is searching for an unknown \textit{target function} $f:X \rightarrow Y$ from the input space $X$ to the output space $Y$ \cite{abu2012learning} that represents an ideal way of identifying iris species. $X$ denotes the possible inputs, in this case all combinations of the four features that have been defined, whereas $Y$ are the outputs, here the species of iris plant. The examples that the gardener recorded are samples $(x_1,y_1),(x_2,y_2),\dots,(x_n,y_n)$ from $f$ such that $f(x_i)=y_i$. Together, they form a data set $D$ which is one of all possible data sets $\mathbb{D}$ for the problem. They then choose a specific approximation $g:X \rightarrow Y,g\approx f$, the decision tree they built, from the hypothesis space $H$, which in this case consists of possible decision trees. The learning algorithm itself thus maps a data set to a hypothesis from the hypothesis space and can be defined as $A:\mathbb{D}\rightarrow H$.

\begin{figure}
\includegraphics[width=\textwidth]{gfx/placeholder_learning}
\caption{PLACEHOLDER: The learning problem, adapted from \cite{abu2012learning}}
\label{fig:learning_problem}
\end{figure}

@@

general measure predictive accuracy (e.g. go back to example gardener model is not perfect so miss classifies some instancs if want to know how good exactly, how find out?
